### 2017-09-19 Docs/Thesis/docs/chapter4.tex
**IMPORTANTE MODIFICATIONS**: now the Prototypes/ dir is removed, and all simulations and validation tests are unther Tests/ and are in a Python project format

\begin{table}[ht!]
	\centering
	\caption{Stack of models used to create the CTD file}
	\label{tab:mehtods}
	\begin{tabular}{|l|l|}
		\hline
		Link Layer                          & \multirow{3}{*}{Packets header's data} \\ \cline{1-1}
		Network Layer                       &                                       \\ \cline{1-1}
		Transport Layer                     &                                       \\ \hline
		Application Layer                   & Application Match Table                    \\ \hline
		\multirow{2}{*}{Inter Packet Times} & Algorithm: $calcOnOff$                             \\ \cline{2-2} 
		& 
		Algorithm: $stochasticModelFitting$                    \\ \hline
		Packet Sizes                        & Algorithm: $stochasticModelFitting$                    \\ \hline
	\end{tabular}
\end{table}

>>>>

\begin{table}[ht!]
	\centering
	\caption{Stack of models used to create the CTD file}
	\label{tab:mehtods}
	\begin{tabular}{|l|l|l|}
		\hline
		Layer & Method & Variables \\
		\hline
		Link Layer  & \multirow{3}{*}{Packets header's data} & \texttt{link\_layer}, \texttt{link\_layer.mac\_src}, \texttt{link\_layer.mac\_dst} \\ \cline{1-1}\cline{3-3}

		Network Layer & & \texttt{network\_layer}, \texttt{network\_layer.src\_ip}, \texttt{network\_layer.dst\_ip}, \texttt{network\_layer.ttl},\texttt{}\\ \cline{1-1}\cline{3-3}

		Transport Layer & & \texttt{transport\_layer}, \texttt{transport\_layer.dst\_port}, \texttt{transport\_layer.src\_port}\\ \hline

		Application Layer  & Application Match Table  & \texttt{application\_layer} \\ \hline

		\multirow{2}{*}{Inter Packet Times} & Algorithm: $calcOnOff$  & \texttt{inter\_packet\_times}\\ 
		\cline{2-2}\cline{3-3}  & Algorithm: $stochasticModelFitting$                    &\\  \hline
		Packet Sizes  & Algorithm: $stochasticModelFitting$ &\\ \hline
	\end{tabular}
\end{table}
